---
title: "Hypoxia and Cognitive Ability in Humans: A Systematic Review and Meta-Analysis - Supplementary Material"
author: "Daniel J McKeown"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: false
    number_sections: false
---

This report presents the results of a series of meta-analytic models examining the effects of hypoxia on cognitive performance. For each cognitive domain, two models are presented, as well as a funnel plot and a model accounting for publication bias:

- **Main effect model**: Estimates the overall effect of hypoxia on the cognitive outcome across studies, without accounting for additional predictors.
- **Moderator model**: Includes study-level moderators (e.g., severity , duration, and type of exposure, cognitive domain/task measure, and participant age) to examine whether these factors explain variability in effect sizes across studies.
- **Funnel plot**: Funnel plots are also included to visualise the distribution of effect sizes included in each model.
- **Corrected model**: To control for potentional publication bias, the main effect model was corrected using the trimfill function of the metafor package.

All models were fit using the `metafor` package in R, with standardized mean differences (SMDH) as the effect size metric and random effects specified at the study level.

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,     # hides code
  message = FALSE,
  warning = FALSE
)
library(metafor)
library(readr)
library(dplyr)
library(knitr)
library(kableExtra)  # for prettier tables
```


```{r}
cog_ability <- read_csv("C:/Users/Hypox//OneDrive - Bond University//OXYNAV//2025//Systematic review//cog_ability_meta.csv")

#Filter Malle et al., 2013 due to being an outlier
cog_ability_filt <- cog_ability[!grepl("Malle et al., 2013", cog_ability$study), ]

# Log transform Duration (adding 1 to avoid log(0))
cog_ability_filt$log_duration <- log(cog_ability_filt$Duration + 1)
```

**Cognitive Ability Domain**
```{r}
# Model with no moderators
cog_meta_red <- rma(m1i = Mean.2,
                    m2i = Mean.1,
                    sd1i = SD.2,
                    sd2i = SD.1,
                    n1i = N.2,
                    n2i = N.1,
                    measure = "SMDH",
                    data = cog_ability_filt,
                    method = "REML")

# Extract the main coefficient table (as a data frame)
model_tbl <- as.data.frame(summary(cog_meta_red)$beta)
colnames(model_tbl) <- "Estimate"

# Combine with SE, zval, pval, ci.lb, ci.ub
model_stats <- data.frame(
  Estimate = summary(cog_meta_red)$beta,
  SE       = summary(cog_meta_red)$se,
  zval     = summary(cog_meta_red)$zval,
  pval     = summary(cog_meta_red)$pval,
  ci.lb    = summary(cog_meta_red)$ci.lb,
  ci.ub    = summary(cog_meta_red)$ci.ub
)

# Round and format nicely
model_stats <- round(model_stats, 3)

# Display with kable
kable(model_stats, caption = "Reduced Model Main Effect") %>%
  kable_styling(latex_options = c("striped", "hold_position"))


model_data <- escalc(measure = "SMDH", 
                  m1i = Mean.2, sd1i = SD.2, n1i = N.2, 
                  m2i = Mean.1, sd2i = SD.1, n2i = N.1,
                  slab = paste(study),
                  data = cog_ability_filt,
                  var.names = c("SMDH", "SMDH_var"))

cog_meta_full <- rma.mv(SMDH, SMDH_var,
              mods = ~ Severity + log_duration + Age + domain,
              random = ~ 1 | study,
              data = model_data,
              method = "REML")

# Get the model summary
summary_full <- summary(cog_meta_full)

# Extract moderator info
mod_results <- data.frame(
  Estimate = summary_full$beta[,1],
  SE = summary_full$se,
  zval = summary_full$zval,
  pval = summary_full$pval,
  CI_Lower = summary_full$ci.lb,
  CI_Upper = summary_full$ci.ub
)
rownames(mod_results) <- gsub("log_duration", "Duration ", rownames(mod_results))
rownames(mod_results) <- gsub("domain", "Domain: ", rownames(mod_results))

# Round for presentation
mod_results <- mod_results %>%
  mutate(across(where(is.numeric), round, digits = 3))

# Show as table
kable(mod_results, caption = "Full Model Moderator Effects") %>%
  kable_styling(latex_options = c("striped", "hold_position"))

#Funnel plot
funnel.rma(cog_meta_red)

#Corrected trimfill model
tf_model <- trimfill(cog_meta_red)
tf_summary <- summary(tf_model)

# Extract the main coefficient table (as a data frame)
tf_model_tbl <- as.data.frame(tf_summary$beta)
colnames(tf_model_tbl) <- "Estimate"

# Combine with SE, zval, pval, ci.lb, ci.ub
tf_model_stats <- data.frame(
  Estimate = tf_summary$beta,
  SE       = tf_summary$se,
  zval     = tf_summary$zval,
  pval     = tf_summary$pval,
  ci.lb    = tf_summary$ci.lb,
  ci.ub    = tf_summary$ci.ub
)

# Round and format nicely
tf_model_stats <- round(tf_model_stats, 3)

# Display with kable (same style as the reduced model)
kable(tf_model_stats, caption = "Trim and Fill Model Effect") %>%
  kable_styling(latex_options = c("striped", "hold_position"))

```

**Memory Domain**
```{r}
memory_data <- cog_ability_filt %>%
  filter(measure %in% c("working memory (score)", 
                        "learning and memory (score)", 
                        "short-term memory (score)",
                        "associative memory (score)", 
                        "long-term memory (score)", 
                        "involuntary memory (score)", 
                        "visual memory (score)", 
                        "verbal memory (score)", 
                        "episodic memory (score)")
         )


# Compute SMD (Hedges' g) and variance
memory_meta_red <-rma(m1i = Mean.2,
               m2i = Mean.1,
               sd1i = SD.2,
               sd2i = SD.1,
               n1i = N.2,
               n2i = N.1,
               measure = "SMDH",
               data = memory_data,
               method = "REML")

# Extract the main coefficient table (as a data frame)
model_tbl <- as.data.frame(summary(memory_meta_red)$beta)
colnames(model_tbl) <- "Estimate"

# Combine with SE, zval, pval, ci.lb, ci.ub
model_stats <- data.frame(
  Estimate = summary(memory_meta_red)$beta,
  SE       = summary(memory_meta_red)$se,
  zval     = summary(memory_meta_red)$zval,
  pval     = summary(memory_meta_red)$pval,
  ci.lb    = summary(memory_meta_red)$ci.lb,
  ci.ub    = summary(memory_meta_red)$ci.ub
)

# Round and format nicely
model_stats <- round(model_stats, 3)

# Display with kable
kable(model_stats, caption = "Reduced Model Main Effect") %>%
  kable_styling(latex_options = c("striped", "hold_position"))


# Compute SMD (Hedges' g) and variance
model_data <- escalc(measure = "SMDH", 
                  m1i = Mean.2, sd1i = SD.2, n1i = N.2, 
                  m2i = Mean.1, sd2i = SD.1, n2i = N.1,
                  slab = paste(study),
                  data = memory_data,
                  var.names = c("SMDH", "SMDH_var"))

memory_meta_full <- rma.mv(SMDH, SMDH_var,
              mods = ~ Severity + log_duration + T.2 + Age + measure,
              random = ~ 1 | study,
              data = model_data,
              method = "REML")

# Get the model summary
summary_full <- summary(memory_meta_full)

# Extract moderator info
mod_results <- data.frame(
  Estimate = summary_full$beta[,1],
  SE = summary_full$se,
  zval = summary_full$zval,
  pval = summary_full$pval,
  CI_Lower = summary_full$ci.lb,
  CI_Upper = summary_full$ci.ub
)

rownames(mod_results) <- gsub("log_duration", "Duration ", rownames(mod_results))
rownames(mod_results) <- gsub("measure", "Measure: ", rownames(mod_results))
rownames(mod_results) <- gsub("T.2", "Type: ", rownames(mod_results))

# Round for presentation
mod_results <- mod_results %>%
  mutate(across(where(is.numeric), round, digits = 3))

# Show as table
kable(mod_results, caption = "Full Model Moderator Effects") %>%
  kable_styling(latex_options = c("striped", "hold_position"))

funnel.rma(memory_meta_red)

#Corrected trimfill model
tf_model <- trimfill(memory_meta_red)
tf_summary <- summary(tf_model)

# Extract the main coefficient table (as a data frame)
tf_model_tbl <- as.data.frame(tf_summary$beta)
colnames(tf_model_tbl) <- "Estimate"

# Combine with SE, zval, pval, ci.lb, ci.ub
tf_model_stats <- data.frame(
  Estimate = tf_summary$beta,
  SE       = tf_summary$se,
  zval     = tf_summary$zval,
  pval     = tf_summary$pval,
  ci.lb    = tf_summary$ci.lb,
  ci.ub    = tf_summary$ci.ub
)

# Round and format nicely
tf_model_stats <- round(tf_model_stats, 3)

# Display with kable (same style as the reduced model)
kable(tf_model_stats, caption = "Trim and Fill Model Effect") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

**Attention Domain**
```{r}
attention_data <- cog_ability_filt %>%
  filter(measure %in% c("attention/response inhibition (score)")
         )


# Compute SMD (Hedges' g) and variance
attention_meta_red <-rma(m1i = Mean.2,
               m2i = Mean.1,
               sd1i = SD.2,
               sd2i = SD.1,
               n1i = N.2,
               n2i = N.1,
               measure = "SMDH",
               data = attention_data,
               method = "REML")

# Extract the main coefficient table (as a data frame)
model_tbl <- as.data.frame(summary(attention_meta_red)$beta)
colnames(model_tbl) <- "Estimate"

# Combine with SE, zval, pval, ci.lb, ci.ub
model_stats <- data.frame(
  Estimate = summary(attention_meta_red)$beta,
  SE       = summary(attention_meta_red)$se,
  zval     = summary(attention_meta_red)$zval,
  pval     = summary(attention_meta_red)$pval,
  ci.lb    = summary(attention_meta_red)$ci.lb,
  ci.ub    = summary(attention_meta_red)$ci.ub
)

# Round and format nicely
model_stats <- round(model_stats, 3)

# Display with kable
kable(model_stats, caption = "Reduced Model Main Effect") %>%
  kable_styling(latex_options = c("striped", "hold_position"))


# Compute SMD (Hedges' g) and variance
model_data <- escalc(measure = "SMDH", 
                  m1i = Mean.2, sd1i = SD.2, n1i = N.2, 
                  m2i = Mean.1, sd2i = SD.1, n2i = N.1,
                  slab = paste(study),
                  data = attention_data,
                  var.names = c("SMDH", "SMDH_var"))

attention_meta_full <- rma.mv(SMDH, SMDH_var,
              mods = ~ Severity + log_duration + T.2 + Age,
              random = ~ 1 | study,
              data = model_data,
              method = "REML")

# Get the model summary
summary_full <- summary(attention_meta_full)

# Extract moderator info
mod_results <- data.frame(
  Estimate = summary_full$beta[,1],
  SE = summary_full$se,
  zval = summary_full$zval,
  pval = summary_full$pval,
  CI_Lower = summary_full$ci.lb,
  CI_Upper = summary_full$ci.ub
)

rownames(mod_results) <- gsub("log_duration", "Duration ", rownames(mod_results))
rownames(mod_results) <- gsub("T.2", "Type: ", rownames(mod_results))

# Round for presentation
mod_results <- mod_results %>%
  mutate(across(where(is.numeric), round, digits = 3))

# Show as table
kable(mod_results, caption = "Full Model Moderator Effects") %>%
  kable_styling(latex_options = c("striped", "hold_position"))

funnel(attention_meta_red)

#Corrected trimfill model
tf_model <- trimfill(attention_meta_red)
tf_summary <- summary(tf_model)

# Extract the main coefficient table (as a data frame)
tf_model_tbl <- as.data.frame(tf_summary$beta)
colnames(tf_model_tbl) <- "Estimate"

# Combine with SE, zval, pval, ci.lb, ci.ub
tf_model_stats <- data.frame(
  Estimate = tf_summary$beta,
  SE       = tf_summary$se,
  zval     = tf_summary$zval,
  pval     = tf_summary$pval,
  ci.lb    = tf_summary$ci.lb,
  ci.ub    = tf_summary$ci.ub
)

# Round and format nicely
tf_model_stats <- round(tf_model_stats, 3)

# Display with kable (same style as the reduced model)
kable(tf_model_stats, caption = "Trim and Fill Model Effect") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

**Executive Function Domain**
```{r}
executive_data <- cog_ability_filt%>%
  filter(measure %in% c("executive function (score)", "verbal fluency (score)", "non-verbal fluency (score)", "tower task (score)", "cognitive flexibility (score)", "coding (score)", "decision-making (score)", "visual acuity (score)", "reasoning (score)", "risk-taking (score)", "addition (score)", "incorrect answers (score)", "neurocognitive index (score)", "pattern recognition (score)", "number comparison (score)", "proof-reading (score)", "spatial tracking (score)", "map compass (score)" ))


# Compute SMD (Hedges' g) and variance
executive_meta_red <-rma(m1i = Mean.2,
               m2i = Mean.1,
               sd1i = SD.2,
               sd2i = SD.1,
               n1i = N.2,
               n2i = N.1,
               measure = "SMDH",
               data = executive_data,
               method = "REML")

# Extract the main coefficient table (as a data frame)
model_tbl <- as.data.frame(summary(executive_meta_red)$beta)
colnames(model_tbl) <- "Estimate"

# Combine with SE, zval, pval, ci.lb, ci.ub
model_stats <- data.frame(
  Estimate = summary(executive_meta_red)$beta,
  SE       = summary(executive_meta_red)$se,
  zval     = summary(executive_meta_red)$zval,
  pval     = summary(executive_meta_red)$pval,
  ci.lb    = summary(executive_meta_red)$ci.lb,
  ci.ub    = summary(executive_meta_red)$ci.ub
)

# Round and format nicely
model_stats <- round(model_stats, 3)

# Display with kable
#kable(model_stats, caption = "Reduced Model Main Effect") %>%
  #kable_styling(latex_options = c("striped", "hold_position"))


# Compute SMD (Hedges' g) and variance
model_data <- escalc(measure = "SMDH", 
                  m1i = Mean.2, sd1i = SD.2, n1i = N.2, 
                  m2i = Mean.1, sd2i = SD.1, n2i = N.1,
                  slab = paste(study),
                  data = executive_data,
                  var.names = c("SMDH", "SMDH_var"))

executive_meta_full <- rma.mv(SMDH, SMDH_var,
              mods = ~ Severity + log_duration + T.2 + Age + measure,
              random = ~ 1 | study,
              data = model_data,
              method = "REML")

# Get the model summary
summary_full <- summary(executive_meta_full)

# Extract moderator info
mod_results <- data.frame(
  Estimate = summary_full$beta[,1],
  SE = summary_full$se,
  zval = summary_full$zval,
  pval = summary_full$pval,
  CI_Lower = summary_full$ci.lb,
  CI_Upper = summary_full$ci.ub
)

rownames(mod_results) <- gsub("log_duration", "Duration ", rownames(mod_results))
rownames(mod_results) <- gsub("measure", "Measure: ", rownames(mod_results))
rownames(mod_results) <- gsub("T.2", "Type: ", rownames(mod_results))

# Round for presentation
mod_results <- mod_results %>%
  mutate(across(where(is.numeric), round, digits = 3))

# Show as table
#kable(mod_results, caption = "Full Model Moderator Effects") %>%
  #kable_styling(latex_options = c("striped", "hold_position"))

funnel(executive_meta_red)

#Corrected trimfill model
tf_model <- trimfill(executive_meta_red)
tf_summary <- summary(tf_model)

# Extract the main coefficient table (as a data frame)
tf_model_tbl <- as.data.frame(tf_summary$beta)
colnames(tf_model_tbl) <- "Estimate"

# Combine with SE, zval, pval, ci.lb, ci.ub
tf_model_stats <- data.frame(
  Estimate = tf_summary$beta,
  SE       = tf_summary$se,
  zval     = tf_summary$zval,
  pval     = tf_summary$pval,
  ci.lb    = tf_summary$ci.lb,
  ci.ub    = tf_summary$ci.ub
)

# Round and format nicely
tf_model_stats <- round(tf_model_stats, 3)

# Display with kable (same style as the reduced model)
#kable(tf_model_stats, caption = "Trim and Fill Model Effect") %>%
  #kable_styling(latex_options = c("striped", "hold_position"))
```

**Processing Speed Domain**
```{r}
process_data <- cog_ability_filt %>%
  filter(measure %in% c("processing speed (milliseconds)"))


# Compute SMD (Hedges' g) and variance
process_meta_red <-rma(m1i = Mean.2,
               m2i = Mean.1,
               sd1i = SD.2,
               sd2i = SD.1,
               n1i = N.2,
               n2i = N.1,
               measure = "SMDH",
               data = process_data,
               method = "REML")

# Extract the main coefficient table (as a data frame)
model_tbl <- as.data.frame(summary(process_meta_red)$beta)
colnames(model_tbl) <- "Estimate"

# Combine with SE, zval, pval, ci.lb, ci.ub
model_stats <- data.frame(
  Estimate = summary(process_meta_red)$beta,
  SE       = summary(process_meta_red)$se,
  zval     = summary(process_meta_red)$zval,
  pval     = summary(process_meta_red)$pval,
  ci.lb    = summary(process_meta_red)$ci.lb,
  ci.ub    = summary(process_meta_red)$ci.ub
)

# Round and format nicely
model_stats <- round(model_stats, 3)

# Display with kable
kable(model_stats, caption = "Reduced Model Main Effect") %>%
  kable_styling(latex_options = c("striped", "hold_position"))


# Compute SMD (Hedges' g) and variance
model_data <- escalc(measure = "SMDH", 
                  m1i = Mean.2, sd1i = SD.2, n1i = N.2, 
                  m2i = Mean.1, sd2i = SD.1, n2i = N.1,
                  slab = paste(study),
                  data = process_data,
                  var.names = c("SMDH", "SMDH_var"))

process_meta_full <- rma.mv(SMDH, SMDH_var,
              mods = ~ Severity + log_duration + T.2 + Age,
              random = ~ 1 | study,
              data = model_data,
              method = "REML")

# Get the model summary
summary_full <- summary(process_meta_full)

# Extract moderator info
mod_results <- data.frame(
  Estimate = summary_full$beta[,1],
  SE = summary_full$se,
  zval = summary_full$zval,
  pval = summary_full$pval,
  CI_Lower = summary_full$ci.lb,
  CI_Upper = summary_full$ci.ub
)

rownames(mod_results) <- gsub("log_duration", "Duration ", rownames(mod_results))
rownames(mod_results) <- gsub("T.2", "Type: ", rownames(mod_results))

# Round for presentation
mod_results <- mod_results %>%
  mutate(across(where(is.numeric), round, digits = 3))

# Show as table
kable(mod_results, caption = "Full Model Moderator Effects") %>%
  kable_styling(latex_options = c("striped", "hold_position"))

funnel(process_meta_red)

#Corrected trimfill model
tf_model <- trimfill(process_meta_red)
tf_summary <- summary(tf_model)

# Extract the main coefficient table (as a data frame)
tf_model_tbl <- as.data.frame(tf_summary$beta)
colnames(tf_model_tbl) <- "Estimate"

# Combine with SE, zval, pval, ci.lb, ci.ub
tf_model_stats <- data.frame(
  Estimate = tf_summary$beta,
  SE       = tf_summary$se,
  zval     = tf_summary$zval,
  pval     = tf_summary$pval,
  ci.lb    = tf_summary$ci.lb,
  ci.ub    = tf_summary$ci.ub
)

# Round and format nicely
tf_model_stats <- round(tf_model_stats, 3)

# Display with kable (same style as the reduced model)
kable(tf_model_stats, caption = "Trim and Fill Model Effect") %>%
  kable_styling(latex_options = c("striped", "hold_position"))

```

**Psychomotor Speed Domain**
```{r}
psycho_data <- cog_ability_filt %>%
  filter(measure %in% c("psychomotor speed (score)", "motor speed (score)", "accuracy (score)", "fine-motor control (score"))


# Compute SMD (Hedges' g) and variance
psycho_meta_red <-rma(m1i = Mean.2,
               m2i = Mean.1,
               sd1i = SD.2,
               sd2i = SD.1,
               n1i = N.2,
               n2i = N.1,
               measure = "SMDH",
               data = psycho_data,
               method = "REML")

# Extract the main coefficient table (as a data frame)
model_tbl <- as.data.frame(summary(psycho_meta_red)$beta)
colnames(model_tbl) <- "Estimate"

# Combine with SE, zval, pval, ci.lb, ci.ub
model_stats <- data.frame(
  Estimate = summary(psycho_meta_red)$beta,
  SE       = summary(psycho_meta_red)$se,
  zval     = summary(psycho_meta_red)$zval,
  pval     = summary(psycho_meta_red)$pval,
  ci.lb    = summary(psycho_meta_red)$ci.lb,
  ci.ub    = summary(psycho_meta_red)$ci.ub
)

# Round and format nicely
model_stats <- round(model_stats, 3)

# Display with kable
kable(model_stats, caption = "Reduced Model Main Effect") %>%
  kable_styling(latex_options = c("striped", "hold_position"))


# Compute SMD (Hedges' g) and variance
model_data <- escalc(measure = "SMDH", 
                  m1i = Mean.2, sd1i = SD.2, n1i = N.2, 
                  m2i = Mean.1, sd2i = SD.1, n2i = N.1,
                  slab = paste(study),
                  data = psycho_data,
                  var.names = c("SMDH", "SMDH_var"))

psycho_meta_full <- rma.mv(SMDH, SMDH_var,
              mods = ~ Severity + log_duration + T.2 + Age + measure,
              random = ~ 1 | study,
              data = model_data,
              method = "REML")

# Get the model summary
summary_full <- summary(psycho_meta_full)

# Extract moderator info
mod_results <- data.frame(
  Estimate = summary_full$beta[,1],
  SE = summary_full$se,
  zval = summary_full$zval,
  pval = summary_full$pval,
  CI_Lower = summary_full$ci.lb,
  CI_Upper = summary_full$ci.ub
)

rownames(mod_results) <- gsub("log_duration", "Duration ", rownames(mod_results))
rownames(mod_results) <- gsub("measure", "Measure: ", rownames(mod_results))
rownames(mod_results) <- gsub("T.2", "Type: ", rownames(mod_results))

# Round for presentation
mod_results <- mod_results %>%
  mutate(across(where(is.numeric), round, digits = 3))

# Show as table
kable(mod_results, caption = "Full Model Moderator Effects") %>%
  kable_styling(latex_options = c("striped", "hold_position"))

funnel(psycho_meta_red)

#Corrected trimfill model
tf_model <- trimfill(psycho_meta_red)
tf_summary <- summary(tf_model)

# Extract the main coefficient table (as a data frame)
tf_model_tbl <- as.data.frame(tf_summary$beta)
colnames(tf_model_tbl) <- "Estimate"

# Combine with SE, zval, pval, ci.lb, ci.ub
tf_model_stats <- data.frame(
  Estimate = tf_summary$beta,
  SE       = tf_summary$se,
  zval     = tf_summary$zval,
  pval     = tf_summary$pval,
  ci.lb    = tf_summary$ci.lb,
  ci.ub    = tf_summary$ci.ub
)

# Round and format nicely
tf_model_stats <- round(tf_model_stats, 3)

# Display with kable (same style as the reduced model)
kable(tf_model_stats, caption = "Trim and Fill Model Effect") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```