---
title: 'Neurocognitive Vulnerability During Hypoxia: Differential Effects Across Cognitive
  Domains'
author: "Daniel J McKeown"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: false
    df_print: paged
  pdf_document:
    toc: false
    number_sections: false
---

This report presents the results of a series of meta-analytic models examining the effects of hypoxia on cognitive performance. For each cognitive domain, two models are presented, as well as a funnel plot and a model accounting for publication bias:

- **Main effect model**: Estimates the overall effect of hypoxia on the cognitive outcome across studies, without accounting for additional predictors.
- **Moderator model**: Includes study-level moderators (e.g., severity , duration, and type of exposure, cognitive domain/task measure, and participant age) to examine whether these factors explain variability in effect sizes across studies.
- **Funnel plot**: Funnel plots are also included to visualise the distribution of effect sizes included in each model.
- **Corrected model**: To control for potentional publication bias, the main effect model was corrected using the trimfill function of the metafor package.

All models were fit using the `metafor` package in R, with standardized mean differences (SMDH) as the effect size metric and random effects specified at the study level.

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,     # hides code
  message = FALSE,
  warning = FALSE
)
library(metafor)
library(readr)
library(dplyr)
library(knitr)
library(kableExtra)  # for prettier tables
```

```{r}
cog_ability <- read_csv("data/cog_ability_meta.csv")

#Filter Malle et al., 2013 due to being an outlier
cog_ability_filt <- cog_ability[!grepl("Malle et al., 2013", cog_ability$study), ]

# Log transform Duration (adding 1 to avoid log(0))
cog_ability_filt$log_duration <- log(cog_ability_filt$Duration + 1)
```

#Categorise variables where needed
```{r}
# Prepare moderator variables
cog_ability_filt$chc_broad <- factor(cog_ability_filt$chc_ability)
cog_ability_filt$T.2 <- factor(cog_ability_filt$T.2)

# Mean-centre continuous moderators
cog_ability_filt$Severity_c <- scale(
  cog_ability_filt$Severity,
  center = TRUE,
  scale = FALSE
)

cog_ability_filt$log_duration_c <- scale(
  cog_ability_filt$log_duration,
  center = TRUE,
  scale = FALSE
)

cog_ability_filt$Age_c <- scale(
  cog_ability_filt$Age,
  center = TRUE,
  scale = FALSE
)
```

```{r}
cog_ability_filt %>%
  group_by(chc_code) %>%
  summarise(
    k = n(),
    studies = n_distinct(study),
    .groups = "drop"
  ) %>%
  arrange(chc_code) %>%
  kable(
    caption = "Effect Sizes and Studies by CHC Broad Ability"
  )
```


#Overall cognitive ability

```{r}

# ============================================================
# OVERALL COGNITIVE ABILITY META-ANALYSIS
# ============================================================


# ============================================================
# MAIN RANDOM-EFFECTS MODEL
# ============================================================

cog_meta_red <- rma(
  yi = yi,
  vi = vi,
  data = cog_ability_filt,
  method = "REML"
)


# ============================================================
# MAIN EFFECT RESULTS
# ============================================================

summary_red <- summary(cog_meta_red)

model_stats <- data.frame(
  Estimate = as.numeric(summary_red$beta),
  SE = summary_red$se,
  zval = summary_red$zval,
  pval = summary_red$pval,
  CI_Lower = summary_red$ci.lb,
  CI_Upper = summary_red$ci.ub
)

rownames(model_stats) <- "Overall Effect"

model_stats <- model_stats %>%
  mutate(
    across(
      where(is.numeric),
      ~ round(.x, 3)
    )
  )

kable(
  model_stats,
  caption = "Random-Effects Model: Overall Cognitive Ability"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# HETEROGENEITY STATISTICS
# ============================================================

heterogeneity_stats <- data.frame(
  
  Effect_Sizes = cog_meta_red$k,
  
  Tau2 = cog_meta_red$tau2,
  
  Tau = sqrt(cog_meta_red$tau2),
  
  I2 = cog_meta_red$I2,
  
  H2 = cog_meta_red$H2,
  
  Q = cog_meta_red$QE,
  
  df = cog_meta_red$k - cog_meta_red$p,
  
  p_value = cog_meta_red$QEp
)

heterogeneity_stats <- heterogeneity_stats %>%
  mutate(
    across(
      where(is.numeric),
      ~ round(.x, 3)
    )
  )

kable(
  heterogeneity_stats,
  caption = "Heterogeneity Statistics"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# PREDICTION INTERVAL
# ============================================================

# The prediction interval estimates the expected range of
# true effects in a future comparable study.

pred_red <- predict(
  cog_meta_red,
  level = 95
)

prediction_interval <- data.frame(
  
  Pooled_Effect = pred_red$pred,
  
  CI_Lower = pred_red$ci.lb,
  
  CI_Upper = pred_red$ci.ub,
  
  PI_Lower = pred_red$pi.lb,
  
  PI_Upper = pred_red$pi.ub
)

prediction_interval <- prediction_interval %>%
  mutate(
    across(
      where(is.numeric),
      ~ round(.x, 3)
    )
  )

kable(
  prediction_interval,
  caption = "Pooled Effect and 95 Percent Prediction Interval"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# FULL MULTILEVEL MODERATOR MODEL
# ============================================================

cog_meta_full <- rma.mv(
  yi,
  vi,
  mods = ~ Severity_c +
    log_duration_c +
    Age_c +
    chc_broad +
    T.2,
  random = ~ 1 | study,
  data = cog_ability_filt,
  method = "REML"
)


# ============================================================
# EXTRACT MODERATOR MODEL RESULTS
# ============================================================

summary_full <- summary(cog_meta_full)

mod_results <- data.frame(
  
  Term = rownames(summary_full$beta),
  
  Estimate = as.numeric(summary_full$beta),
  
  SE = summary_full$se,
  
  zval = summary_full$zval,
  
  pval = summary_full$pval,
  
  CI_Lower = summary_full$ci.lb,
  
  CI_Upper = summary_full$ci.ub
)


# ============================================================
# IMPROVE COEFFICIENT LABELS
# ============================================================

mod_results$Term <- gsub(
  "intrcpt",
  "Intercept",
  mod_results$Term
)

mod_results$Term <- gsub(
  "Severity_c",
  "Hypoxia Severity",
  mod_results$Term
)

mod_results$Term <- gsub(
  "log_duration_c",
  "Log Duration",
  mod_results$Term
)

mod_results$Term <- gsub(
  "Age_c",
  "Participant Age",
  mod_results$Term
)

mod_results$Term <- gsub(
  "chc_broad",
  "Cognitive Ability: ",
  mod_results$Term
)

mod_results$Term <- gsub(
  "T.2",
  "Hypoxia Type: ",
  mod_results$Term
)


# ============================================================
# ROUND MODERATOR RESULTS
# ============================================================

mod_results <- mod_results %>%
  mutate(
    across(
      where(is.numeric),
      ~ round(.x, 3)
    )
  )


# ============================================================
# DISPLAY MODERATOR RESULTS
# ============================================================

kable(
  mod_results,
  caption = "Multilevel Moderator Model"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# OMNIBUS TEST OF MODERATORS
# ============================================================

# QM tests whether the included moderators collectively
# explain a significant amount of variability in effect sizes.

moderator_test <- data.frame(
  
  QM = cog_meta_full$QM,
  
  df = cog_meta_full$m,
  
  p_value = cog_meta_full$QMp
)

moderator_test <- moderator_test %>%
  mutate(
    across(
      where(is.numeric),
      ~ round(.x, 3)
    )
  )

kable(
  moderator_test,
  caption = "Omnibus Test of Moderators"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# RESIDUAL HETEROGENEITY
# ============================================================

# QE tests whether significant heterogeneity remains after
# accounting for the included moderators.

residual_heterogeneity <- data.frame(
  
  QE = cog_meta_full$QE,
  
  df = cog_meta_full$k - cog_meta_full$p,
  
  p_value = cog_meta_full$QEp
)

residual_heterogeneity <- residual_heterogeneity %>%
  mutate(
    across(
      where(is.numeric),
      ~ round(.x, 3)
    )
  )

kable(
  residual_heterogeneity,
  caption = "Residual Heterogeneity in the Moderator Model"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# FUNNEL PLOT
# ============================================================

funnel(
  cog_meta_red,
  main = "Funnel Plot: Overall Cognitive Ability"
)


# ============================================================
# TRIM-AND-FILL MODEL
# ============================================================

tf_model <- trimfill(
  cog_meta_red
)

tf_summary <- summary(
  tf_model
)


# ============================================================
# EXTRACT TRIM-AND-FILL RESULTS
# ============================================================

tf_model_stats <- data.frame(
  
  Estimate = as.numeric(tf_summary$beta),
  
  SE = tf_summary$se,
  
  zval = tf_summary$zval,
  
  pval = tf_summary$pval,
  
  CI_Lower = tf_summary$ci.lb,
  
  CI_Upper = tf_summary$ci.ub
)

rownames(tf_model_stats) <- "Trim-and-Fill Adjusted Effect"

tf_model_stats <- tf_model_stats %>%
  mutate(
    across(
      where(is.numeric),
      ~ round(.x, 3)
    )
  )

kable(
  tf_model_stats,
  caption = "Trim-and-Fill Corrected Model"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# NUMBER OF IMPUTED EFFECT SIZES
# ============================================================

trimfill_info <- data.frame(
  
  Original_Effect_Sizes = cog_meta_red$k,
  
  Imputed_Effect_Sizes = tf_model$k0,
  
  Total_Effect_Sizes = cog_meta_red$k + tf_model$k0
)

kable(
  trimfill_info,
  caption = "Trim-and-Fill Imputation Results"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )
```
  
#FIGURE 1#
```{r}
# ============================================================
# FOREST PLOT: GENERAL COGNITIVE ABILITY
# ============================================================

# Ensure the overall random-effects model exists
cog_meta_red <- rma(
  yi = yi,
  vi = vi,
  data = cog_ability_filt,
  method = "REML"
)


# ------------------------------------------------------------
# Prepare data
# ------------------------------------------------------------

k <- nrow(cog_ability_filt)

# Split into two approximately equal parts
half <- ceiling(k / 2)

cog_data_p1 <- cog_ability_filt[1:half, ]

cog_data_p2 <- cog_ability_filt[
  (half + 1):k,
]


# Create informative labels
cog_data_p1$label <- paste0(
  cog_data_p1$study,
  " (",
  cog_data_p1$chc_ability,
  ")"
)

cog_data_p2$label <- paste0(
  cog_data_p2$study,
  " (",
  cog_data_p2$chc_ability,
  ")"
)


# ============================================================
# FUNCTION TO CREATE EACH FOREST PLOT
# ============================================================

create_forest_plot <- function(data, filename, page_number) {

  k_page <- nrow(data)

  # Give each study a row
  # Reserve rows 1-3 for the overall effect
  study_rows <- seq(
    k_page + 3,
    4,
    by = -1
  )

  pdf(
    filename,
    width = 11,
    height = 14
  )

  # Plot margins
  par(
    mar = c(4, 1, 2, 2)
  )

  forest(

    # Effect sizes
    x = data$yi,

    # Sampling variances
    vi = data$vi,

    # Study labels
    slab = data$label,

    # Row positions
    rows = study_rows,

    # Font size
    cex = 0.65,

    # Overall plotting region
    # Widened to prevent overlap
    xlim = c(-5.5, 3.5),

    # Actual effect-size axis range
    alim = c(-3, 2),

    # Position of study labels and effect size text
    textpos = c(-5.3, 3.3),

    # Suppress automatic summary polygon
    addfit = FALSE,

    # X-axis label
    xlab = "Effect size (Hedges' g)",

    # Consistent axis ticks
    at = c(-3, -2, -1, 0, 1, 2),

    # Header
    header = c(
      paste0(
        "Study / Cognitive ability (Part ",
        page_number,
        ")"
      ),
      "Hedges' g [95% CI]"
    )
  )


  # ----------------------------------------------------------
  # Add zero reference line
  # ----------------------------------------------------------

  abline(
    v = 0,
    lty = 2
  )


  # ----------------------------------------------------------
  # Add overall pooled effect
  # ----------------------------------------------------------

  addpoly(
    cog_meta_red,

    row = 1,

    mlab = "Overall pooled effect",

    cex = 0.75
  )


  # Add a separator above the pooled effect
  abline(
    h = 2.5,
    lty = 3
  )


  dev.off()
}


# ============================================================
# CREATE PART 1
# ============================================================

create_forest_plot(
  data = cog_data_p1,
  filename = "Forest_Plot_Cognitive_Ability_Part1.pdf",
  page_number = 1
)


# ============================================================
# CREATE PART 2
# ============================================================

create_forest_plot(
  data = cog_data_p2,
  filename = "Forest_Plot_Cognitive_Ability_Part2.pdf",
  page_number = 2
)
```


#FIGURE 2#
```{r}
# ============================================================
# META-REGRESSION FIGURE:
# RELATIONSHIP BETWEEN FiO2 AND COGNITIVE EFFECT SIZE
# ============================================================


# ------------------------------------------------------------
# Load required packages
# ------------------------------------------------------------

library(ggplot2)
library(dplyr)
library(scales)


# ------------------------------------------------------------
# 1. Extract the exact coefficient names from the fitted model
# ------------------------------------------------------------

coef_names <- names(coef(cog_meta_full))

# Remove the intercept to obtain the moderator names required
# for the prediction matrix

mod_names <- coef_names[coef_names != "intrcpt"]


# ------------------------------------------------------------
# 2. Define the observed FiO2 range
# ------------------------------------------------------------

fio2_min <- min(
  cog_ability_filt$Severity,
  na.rm = TRUE
)

fio2_max <- max(
  cog_ability_filt$Severity,
  na.rm = TRUE
)


# ------------------------------------------------------------
# 3. Calculate the mean used to centre Severity
# ------------------------------------------------------------

severity_mean <- mean(
  cog_ability_filt$Severity,
  na.rm = TRUE
)


# ------------------------------------------------------------
# 4. Create prediction data
# ------------------------------------------------------------

# Generate 200 values across the observed FiO2 range

pred_data <- data.frame(
  
  Severity = seq(
    from = fio2_min,
    to = fio2_max,
    length.out = 200
  )
)


# Convert raw FiO2 values to the centred Severity variable
# used in the fitted meta-regression

pred_data$Severity_c <- 
  pred_data$Severity - severity_mean


# ------------------------------------------------------------
# 5. Create prediction moderator matrix
# ------------------------------------------------------------

# Create a matrix with exactly the same moderator names
# and ordering as the fitted cog_meta_full model.
#
# All moderators are initially set to zero:
#
# - log_duration_c = 0 -> mean log-transformed duration
# - Age_c = 0 -> mean age
# - factor dummy variables = 0 -> reference categories
#
# Severity_c is then allowed to vary across its observed range.

X_new <- matrix(
  0,
  nrow = nrow(pred_data),
  ncol = length(mod_names)
)

colnames(X_new) <- mod_names


# ------------------------------------------------------------
# 6. Insert varying centred Severity values
# ------------------------------------------------------------

severity_col <- which(
  colnames(X_new) == "Severity_c"
)


# Stop with a clear error if the severity moderator
# cannot be identified

if (length(severity_col) != 1) {
  
  stop(
    "Could not uniquely identify the Severity_c moderator ",
    "in the fitted model."
  )
}


# Insert the centred Severity values into the correct column

X_new[, severity_col] <- pred_data$Severity_c


# ------------------------------------------------------------
# 7. Generate model predictions
# ------------------------------------------------------------

preds <- predict(
  cog_meta_full,
  newmods = X_new
)


# ------------------------------------------------------------
# 8. Add predicted values and 95 Percent confidence intervals
# ------------------------------------------------------------

pred_data$Predicted <- preds$pred

pred_data$CI_Lower <- preds$ci.lb

pred_data$CI_Upper <- preds$ci.ub


# ------------------------------------------------------------
# 9. Create publication-quality figure
# ------------------------------------------------------------

pred_plot <- ggplot() +
  
  
  # ----------------------------------------------------------
  # Observed individual effect sizes
  # ----------------------------------------------------------
  
  # These represent the raw observed Hedges' g values.
  #
  # Semi-transparency is used because multiple effect sizes
  # may overlap at similar FiO2 values.
  
  geom_point(
    data = cog_ability_filt,
    aes(
      x = Severity,
      y = yi
    ),
    colour = "grey40",
    alpha = 0.25,
    size = 1.8
  ) +
  
  
  # ----------------------------------------------------------
  # 95% confidence interval around adjusted prediction
  # ----------------------------------------------------------
  
  geom_ribbon(
    data = pred_data,
    aes(
      x = Severity,
      ymin = CI_Lower,
      ymax = CI_Upper
    ),
    fill = "grey70",
    alpha = 0.40
  ) +
  
  
  # ----------------------------------------------------------
  # Adjusted meta-regression line
  # ----------------------------------------------------------
  
  geom_line(
    data = pred_data,
    aes(
      x = Severity,
      y = Predicted
    ),
    colour = "black",
    linewidth = 1.1
  ) +
  
  
  # ----------------------------------------------------------
  # No-effect reference line
  # ----------------------------------------------------------
  
  geom_hline(
    yintercept = 0,
    linetype = "dashed",
    colour = "grey30",
    linewidth = 0.7
  ) +
  
  
  # ----------------------------------------------------------
  # Axis labels
  # ----------------------------------------------------------
  
  labs(
    x = expression(
      "Fraction of inspired oxygen (" * FiO[2] * ")"
    ),
    
    y = expression(
      "Cognitive effect size (Hedges' " * g * ")"
    )
  ) +
  
  
  # ----------------------------------------------------------
  # X-axis formatting
  # ----------------------------------------------------------
  
  scale_x_continuous(
    limits = c(
      fio2_min,
      fio2_max
    ),
    
    breaks = pretty_breaks(
      n = 6
    ),
    
    labels = label_number(
      accuracy = 0.001
    )
  ) +
  
  
  # ----------------------------------------------------------
  # Publication-style theme
  # ----------------------------------------------------------
  
  theme_classic(
    base_size = 12
  ) +
  
  theme(
    
    axis.title = element_text(
      face = "bold",
      size = 12
    ),
    
    axis.text = element_text(
      size = 11
    ),
    
    axis.line = element_line(
      linewidth = 0.7
    ),
    
    plot.margin = margin(
      t = 10,
      r = 15,
      b = 10,
      l = 15
    )
  )


# ------------------------------------------------------------
# 10. Display figure
# ------------------------------------------------------------

print(pred_plot)


# ------------------------------------------------------------
# 11. Save high-resolution PNG
# ------------------------------------------------------------

ggsave(
  filename = "FiO2_meta_regression.png",
  plot = pred_plot,
  width = 7,
  height = 5,
  units = "in",
  dpi = 600
)


# ------------------------------------------------------------
# 12. Save vector PDF
# ------------------------------------------------------------

ggsave(
  filename = "FiO2_meta_regression.pdf",
  plot = pred_plot,
  width = 7,
  height = 5,
  units = "in"
)
```

# Fluid reasoning ability (Gf)
```{r}

# ============================================================
# FLUID REASONING ABILITY (Gf)
# ============================================================


# -----------------------------
# SUBSET DATA
# -----------------------------

reasoning_data <- cog_ability_filt %>%
  filter(chc_code == "gf")


# Complete-case dataset for duration moderator
reasoning_duration_data <- reasoning_data %>%
  filter(!is.na(log_duration_c))


# ============================================================
# MAIN EFFECT MODEL
# ============================================================

reasoning_meta_red <- rma(
  yi = yi,
  vi = vi,
  data = reasoning_data,
  method = "REML"
)


# -----------------------------
# MAIN EFFECT RESULTS
# -----------------------------

summary_red <- summary(reasoning_meta_red)

model_stats <- data.frame(
  Estimate = as.numeric(summary_red$beta),
  SE = summary_red$se,
  zval = summary_red$zval,
  pval = summary_red$pval,
  CI_Lower = summary_red$ci.lb,
  CI_Upper = summary_red$ci.ub
)

rownames(model_stats) <- "Overall Effect"

model_stats <- model_stats %>%
  mutate(across(where(is.numeric), round, digits = 3))


kable(
  model_stats,
  caption = "Main Effect Model: Fluid Reasoning"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# HETEROGENEITY AND MODEL FIT STATISTICS
# ============================================================

# 95% prediction interval
pred_red <- predict(reasoning_meta_red)


# Number of independent studies
n_studies_reasoning <- n_distinct(reasoning_data$study)


model_fit_stats <- data.frame(
  Effect_Sizes = reasoning_meta_red$k,
  Studies = n_studies_reasoning,
  QE = summary_red$QE,
  QE_df = summary_red$k - summary_red$p,
  QE_p = summary_red$QEp,
  I2 = summary_red$I2,
  H2 = summary_red$H2,
  Tau2 = summary_red$tau2,
  Prediction_Lower = pred_red$pi.lb,
  Prediction_Upper = pred_red$pi.ub,
  AIC = AIC(reasoning_meta_red),
  BIC = BIC(reasoning_meta_red)
)


# Round numerical values
model_fit_stats <- model_fit_stats %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  model_fit_stats,
  caption = "Heterogeneity and Model Fit Statistics: Fluid Reasoning"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# EXPLORATORY UNIVARIABLE MODERATOR MODELS
# ============================================================

# Separate univariable models are used to limit model complexity
# relative to the number of independent studies.


# -----------------------------
# SEVERITY MODERATOR
# -----------------------------

reasoning_severity <- rma.mv(
  yi,
  vi,
  mods = ~ Severity_c,
  random = ~ 1 | study,
  data = reasoning_data,
  method = "REML"
)


# -----------------------------
# DURATION MODERATOR
# -----------------------------

reasoning_duration <- rma.mv(
  yi,
  vi,
  mods = ~ log_duration_c,
  random = ~ 1 | study,
  data = reasoning_duration_data,
  method = "REML"
)


# -----------------------------
# AGE MODERATOR
# -----------------------------

reasoning_age <- rma.mv(
  yi,
  vi,
  mods = ~ Age_c,
  random = ~ 1 | study,
  data = reasoning_data,
  method = "REML"
)


# -----------------------------
# HYPOXIA TYPE MODERATOR
# -----------------------------

reasoning_type <- rma.mv(
  yi,
  vi,
  mods = ~ T.2,
  random = ~ 1 | study,
  data = reasoning_data,
  method = "REML"
)


# ============================================================
# EXTRACT SEVERITY RESULTS
# ============================================================

summary_severity <- summary(reasoning_severity)

severity_results <- data.frame(
  Term = rownames(summary_severity$beta),
  Estimate = summary_severity$beta[, 1],
  SE = summary_severity$se,
  zval = summary_severity$zval,
  pval = summary_severity$pval,
  CI_Lower = summary_severity$ci.lb,
  CI_Upper = summary_severity$ci.ub
)

severity_results$Term <- gsub(
  "intrcpt",
  "Intercept",
  severity_results$Term
)

severity_results$Term <- gsub(
  "Severity_c",
  "Severity",
  severity_results$Term
)

severity_results <- severity_results %>%
  mutate(across(where(is.numeric), round, digits = 3))


# ============================================================
# EXTRACT DURATION RESULTS
# ============================================================

summary_duration <- summary(reasoning_duration)

duration_results <- data.frame(
  Term = rownames(summary_duration$beta),
  Estimate = summary_duration$beta[, 1],
  SE = summary_duration$se,
  zval = summary_duration$zval,
  pval = summary_duration$pval,
  CI_Lower = summary_duration$ci.lb,
  CI_Upper = summary_duration$ci.ub
)

duration_results$Term <- gsub(
  "intrcpt",
  "Intercept",
  duration_results$Term
)

duration_results$Term <- gsub(
  "log_duration_c",
  "Log Duration",
  duration_results$Term
)

duration_results <- duration_results %>%
  mutate(across(where(is.numeric), round, digits = 3))


# ============================================================
# EXTRACT AGE RESULTS
# ============================================================

summary_age <- summary(reasoning_age)

age_results <- data.frame(
  Term = rownames(summary_age$beta),
  Estimate = summary_age$beta[, 1],
  SE = summary_age$se,
  zval = summary_age$zval,
  pval = summary_age$pval,
  CI_Lower = summary_age$ci.lb,
  CI_Upper = summary_age$ci.ub
)

age_results$Term <- gsub(
  "intrcpt",
  "Intercept",
  age_results$Term
)

age_results$Term <- gsub(
  "Age_c",
  "Age",
  age_results$Term
)

age_results <- age_results %>%
  mutate(across(where(is.numeric), round, digits = 3))


# ============================================================
# EXTRACT HYPOXIA TYPE RESULTS
# ============================================================

summary_type <- summary(reasoning_type)

type_results <- data.frame(
  Term = rownames(summary_type$beta),
  Estimate = summary_type$beta[, 1],
  SE = summary_type$se,
  zval = summary_type$zval,
  pval = summary_type$pval,
  CI_Lower = summary_type$ci.lb,
  CI_Upper = summary_type$ci.ub
)

type_results$Term <- gsub(
  "intrcpt",
  "Intercept",
  type_results$Term
)

type_results$Term <- gsub(
  "T.2normobaric hypoxia",
  "Normobaric vs Hypobaric",
  type_results$Term
)

type_results <- type_results %>%
  mutate(across(where(is.numeric), round, digits = 3))


# ============================================================
# COMBINE MODERATOR COEFFICIENT RESULTS
# ============================================================

moderator_results <- bind_rows(
  Severity = severity_results,
  Duration = duration_results,
  Age = age_results,
  Hypoxia_Type = type_results,
  .id = "Moderator_Model"
)


kable(
  moderator_results,
  caption = "Exploratory Univariable Moderator Models: Fluid Reasoning"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position","scale_down")
  )


# ============================================================
# MODERATOR MODEL FIT STATISTICS
# ============================================================

# Helper function to extract model-level statistics

extract_mod_fit <- function(model, data, model_name) {
  
  model_summary <- summary(model)
  
  data.frame(
    Moderator_Model = model_name,
    Effect_Sizes = model$k,
    Studies = n_distinct(data$study),
    QM = model_summary$QM,
    QM_df = model_summary$m,
    QM_p = model_summary$QMp,
    QE = model_summary$QE,
    QE_df = model_summary$k - model_summary$p,
    QE_p = model_summary$QEp,
    Tau2 = sum(model$sigma2),
    AIC = AIC(model),
    BIC = BIC(model)
  )
}


moderator_fit_stats <- bind_rows(
  
  extract_mod_fit(
    reasoning_severity,
    reasoning_data,
    "Severity"
  ),
  
  extract_mod_fit(
    reasoning_duration,
    reasoning_duration_data,
    "Duration"
  ),
  
  extract_mod_fit(
    reasoning_age,
    reasoning_data,
    "Age"
  ),
  
  extract_mod_fit(
    reasoning_type,
    reasoning_data,
    "Hypoxia Type"
  )
)


moderator_fit_stats <- moderator_fit_stats %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  moderator_fit_stats,
  caption = "Model Fit Statistics for Exploratory Univariable Moderator Models"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# NUMBER OF EFFECT SIZES AND STUDIES CONTRIBUTING TO MODELS
# ============================================================

moderator_k <- data.frame(
  
  Model = c(
    "Severity",
    "Duration",
    "Age",
    "Hypoxia Type"
  ),
  
  Effect_Sizes = c(
    nrow(reasoning_data %>% filter(!is.na(Severity_c))),
    nrow(reasoning_duration_data),
    nrow(reasoning_data %>% filter(!is.na(Age_c))),
    nrow(reasoning_data %>% filter(!is.na(T.2)))
  ),
  
  Studies = c(
    
    reasoning_data %>%
      filter(!is.na(Severity_c)) %>%
      summarise(n = n_distinct(study)) %>%
      pull(n),
    
    reasoning_duration_data %>%
      summarise(n = n_distinct(study)) %>%
      pull(n),
    
    reasoning_data %>%
      filter(!is.na(Age_c)) %>%
      summarise(n = n_distinct(study)) %>%
      pull(n),
    
    reasoning_data %>%
      filter(!is.na(T.2)) %>%
      summarise(n = n_distinct(study)) %>%
      pull(n)
  )
)


kable(
  moderator_k,
  caption = "Data Contributing to Exploratory Moderator Models"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# FUNNEL PLOT
# ============================================================

funnel(
  reasoning_meta_red,
  main = "Funnel Plot: Fluid Reasoning (Gf)",
  xlab = "Observed Effect Size (Hedges' g)",
  ylab = "Standard Error",
  refline = 0
)


# ============================================================
# TRIM-AND-FILL MODEL
# ============================================================

tf_model <- trimfill(reasoning_meta_red)

tf_summary <- summary(tf_model)


# -----------------------------
# TRIM-AND-FILL EFFECT
# -----------------------------

tf_model_stats <- data.frame(
  Estimate = as.numeric(tf_summary$beta),
  SE = tf_summary$se,
  zval = tf_summary$zval,
  pval = tf_summary$pval,
  CI_Lower = tf_summary$ci.lb,
  CI_Upper = tf_summary$ci.ub
)

rownames(tf_model_stats) <- "Trim-and-Fill Effect"


tf_model_stats <- tf_model_stats %>%
  mutate(across(where(is.numeric), round, digits = 3))


kable(
  tf_model_stats,
  caption = "Trim-and-Fill Corrected Model: Fluid Reasoning"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# TRIM-AND-FILL IMPUTATION RESULTS
# ============================================================

n_imputed <- ifelse(
  is.null(tf_model$k0),
  0,
  abs(tf_model$k0)
)


trimfill_info <- data.frame(
  Original_Effect_Sizes = reasoning_meta_red$k,
  Imputed_Effect_Sizes = n_imputed,
  Total_Effect_Sizes = reasoning_meta_red$k + n_imputed
)


kable(
  trimfill_info,
  caption = "Trim-and-Fill Imputation Results: Fluid Reasoning"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )
```

# Long-term storage and retrieval ability (Glr)
```{r}
# ============================================================
# LONG-TERM STORAGE AND RETRIEVAL ABILITY (Glr)
# ============================================================


# -----------------------------
# SUBSET DATA
# -----------------------------

retrieval_data <- cog_ability_filt %>%
  filter(chc_code == "glr")


# Complete-case dataset for duration moderator
retrieval_duration_data <- retrieval_data %>%
  filter(!is.na(log_duration_c))


# ============================================================
# MAIN EFFECT MODEL
# ============================================================

retrieval_meta_red <- rma(
  yi = yi,
  vi = vi,
  data = retrieval_data,
  method = "REML"
)


# -----------------------------
# MAIN EFFECT RESULTS
# -----------------------------

summary_red <- summary(retrieval_meta_red)

model_stats <- data.frame(
  Estimate = as.numeric(summary_red$beta),
  SE = summary_red$se,
  zval = summary_red$zval,
  pval = summary_red$pval,
  CI_Lower = summary_red$ci.lb,
  CI_Upper = summary_red$ci.ub
)

rownames(model_stats) <- "Overall Effect"


model_stats <- model_stats %>%
  mutate(across(where(is.numeric), round, digits = 3))


kable(
  model_stats,
  caption = "Main Effect Model: Long-Term Storage and Retrieval"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# HETEROGENEITY AND MODEL FIT STATISTICS
# ============================================================

# 95% prediction interval
pred_red <- predict(retrieval_meta_red)


# Number of independent studies
n_studies_retrieval <- n_distinct(retrieval_data$study)


model_fit_stats <- data.frame(
  Effect_Sizes = retrieval_meta_red$k,
  Studies = n_studies_retrieval,
  QE = summary_red$QE,
  QE_df = summary_red$k - summary_red$p,
  QE_p = summary_red$QEp,
  I2 = summary_red$I2,
  H2 = summary_red$H2,
  Tau2 = summary_red$tau2,
  Prediction_Lower = pred_red$pi.lb,
  Prediction_Upper = pred_red$pi.ub,
  AIC = AIC(retrieval_meta_red),
  BIC = BIC(retrieval_meta_red)
)


model_fit_stats <- model_fit_stats %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  model_fit_stats,
  caption = "Heterogeneity and Model Fit Statistics: Long-Term Storage and Retrieval"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# EXPLORATORY UNIVARIABLE MODERATOR MODELS
# ============================================================

# Separate univariable models are used because of the limited
# number of independent studies within this CHC ability.


# -----------------------------
# SEVERITY MODERATOR
# -----------------------------

retrieval_severity <- rma.mv(
  yi,
  vi,
  mods = ~ Severity_c,
  random = ~ 1 | study,
  data = retrieval_data,
  method = "REML"
)


# -----------------------------
# DURATION MODERATOR
# -----------------------------

retrieval_duration <- rma.mv(
  yi,
  vi,
  mods = ~ log_duration_c,
  random = ~ 1 | study,
  data = retrieval_duration_data,
  method = "REML"
)


# -----------------------------
# AGE MODERATOR
# -----------------------------

retrieval_age <- rma.mv(
  yi,
  vi,
  mods = ~ Age_c,
  random = ~ 1 | study,
  data = retrieval_data,
  method = "REML"
)


# ============================================================
# EXTRACT SEVERITY RESULTS
# ============================================================

summary_severity <- summary(retrieval_severity)

severity_results <- data.frame(
  Term = rownames(summary_severity$beta),
  Estimate = summary_severity$beta[, 1],
  SE = summary_severity$se,
  zval = summary_severity$zval,
  pval = summary_severity$pval,
  CI_Lower = summary_severity$ci.lb,
  CI_Upper = summary_severity$ci.ub
)


severity_results$Term <- gsub(
  "intrcpt",
  "Intercept",
  severity_results$Term
)

severity_results$Term <- gsub(
  "Severity_c",
  "Severity",
  severity_results$Term
)


severity_results <- severity_results %>%
  mutate(across(where(is.numeric), round, digits = 3))


# ============================================================
# EXTRACT DURATION RESULTS
# ============================================================

summary_duration <- summary(retrieval_duration)

duration_results <- data.frame(
  Term = rownames(summary_duration$beta),
  Estimate = summary_duration$beta[, 1],
  SE = summary_duration$se,
  zval = summary_duration$zval,
  pval = summary_duration$pval,
  CI_Lower = summary_duration$ci.lb,
  CI_Upper = summary_duration$ci.ub
)


duration_results$Term <- gsub(
  "intrcpt",
  "Intercept",
  duration_results$Term
)

duration_results$Term <- gsub(
  "log_duration_c",
  "Log Duration",
  duration_results$Term
)


duration_results <- duration_results %>%
  mutate(across(where(is.numeric), round, digits = 3))


# ============================================================
# EXTRACT AGE RESULTS
# ============================================================

summary_age <- summary(retrieval_age)

age_results <- data.frame(
  Term = rownames(summary_age$beta),
  Estimate = summary_age$beta[, 1],
  SE = summary_age$se,
  zval = summary_age$zval,
  pval = summary_age$pval,
  CI_Lower = summary_age$ci.lb,
  CI_Upper = summary_age$ci.ub
)


age_results$Term <- gsub(
  "intrcpt",
  "Intercept",
  age_results$Term
)

age_results$Term <- gsub(
  "Age_c",
  "Age",
  age_results$Term
)


age_results <- age_results %>%
  mutate(across(where(is.numeric), round, digits = 3))


# ============================================================
# COMBINE MODERATOR COEFFICIENT RESULTS
# ============================================================

moderator_results <- bind_rows(
  Severity = severity_results,
  Duration = duration_results,
  Age = age_results,
  .id = "Moderator_Model"
)


kable(
  moderator_results,
  caption = "Exploratory Univariable Moderator Models: Long-Term Storage and Retrieval"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# MODERATOR MODEL FIT STATISTICS
# ============================================================

# Helper function to extract model-level statistics

extract_mod_fit <- function(model, data, model_name) {
  
  model_summary <- summary(model)
  
  data.frame(
    Moderator_Model = model_name,
    Effect_Sizes = model$k,
    Studies = n_distinct(data$study),
    QM = model_summary$QM,
    QM_df = model_summary$m,
    QM_p = model_summary$QMp,
    QE = model_summary$QE,
    QE_df = model_summary$k - model_summary$p,
    QE_p = model_summary$QEp,
    Tau2 = sum(model$sigma2),
    AIC = AIC(model),
    BIC = BIC(model)
  )
}


moderator_fit_stats <- bind_rows(
  
  extract_mod_fit(
    retrieval_severity,
    retrieval_data,
    "Severity"
  ),
  
  extract_mod_fit(
    retrieval_duration,
    retrieval_duration_data,
    "Duration"
  ),
  
  extract_mod_fit(
    retrieval_age,
    retrieval_data,
    "Age"
  )
)


moderator_fit_stats <- moderator_fit_stats %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  moderator_fit_stats,
  caption = "Model Fit Statistics for Exploratory Univariable Moderator Models: Long-Term Storage and Retrieval"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# FUNNEL PLOT
# ============================================================

funnel(
  retrieval_meta_red,
  main = "Funnel Plot: Long-Term Storage and Retrieval (Glr)",
  xlab = "Observed Effect Size (Hedges' g)",
  ylab = "Standard Error",
  refline = 0
)


# ============================================================
# TRIM-AND-FILL MODEL
# ============================================================

tf_model <- trimfill(retrieval_meta_red)

tf_summary <- summary(tf_model)


# -----------------------------
# TRIM-AND-FILL EFFECT
# -----------------------------

tf_model_stats <- data.frame(
  Estimate = as.numeric(tf_summary$beta),
  SE = tf_summary$se,
  zval = tf_summary$zval,
  pval = tf_summary$pval,
  CI_Lower = tf_summary$ci.lb,
  CI_Upper = tf_summary$ci.ub
)

rownames(tf_model_stats) <- "Trim-and-Fill Effect"


tf_model_stats <- tf_model_stats %>%
  mutate(across(where(is.numeric), round, digits = 3))


kable(
  tf_model_stats,
  caption = "Trim-and-Fill Corrected Model: Long-Term Storage and Retrieval"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ============================================================
# TRIM-AND-FILL IMPUTATION RESULTS
# ============================================================

n_imputed <- ifelse(
  is.null(tf_model$k0),
  0,
  abs(tf_model$k0)
)


trimfill_info <- data.frame(
  Original_Effect_Sizes = retrieval_meta_red$k,
  Imputed_Effect_Sizes = n_imputed,
  Total_Effect_Sizes = retrieval_meta_red$k + n_imputed
)


kable(
  trimfill_info,
  caption = "Trim-and-Fill Imputation Results: Long-Term Storage and Retrieval"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )
```

#Psychomotor speed
```{r}
# ==================================================
# PSYCHOMOTOR SPEED (Gps)
# ==================================================

# -----------------------------
# SUBSET DATA
# -----------------------------

psycho_data <- cog_ability_filt %>%
  filter(chc_code == "gps")


# -----------------------------
# MAIN EFFECT MODEL
# -----------------------------

psycho_meta_red <- rma(
  yi = yi,
  vi = vi,
  data = psycho_data,
  method = "REML"
)


# -----------------------------
# MAIN EFFECT RESULTS
# -----------------------------

summary_red <- summary(psycho_meta_red)

model_stats <- data.frame(
  Term = "Overall Effect",
  Estimate = summary_red$beta[, 1],
  SE = summary_red$se,
  zval = summary_red$zval,
  pval = summary_red$pval,
  CI_Lower = summary_red$ci.lb,
  CI_Upper = summary_red$ci.ub
) %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  model_stats,
  caption = "Main Effect Model: Psychomotor Speed"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position","scale_down")
  )


# -----------------------------
# HETEROGENEITY STATISTICS
# -----------------------------

# Prediction interval
pred_red <- predict(
  psycho_meta_red,
  pi = TRUE
)

heterogeneity_stats <- data.frame(
  Effect_Sizes = psycho_meta_red$k,
  Studies = n_distinct(psycho_data$study),
  QE = psycho_meta_red$QE,
  QE_df = psycho_meta_red$k - 1,
  QE_p = psycho_meta_red$QEp,
  I2 = psycho_meta_red$I2,
  Tau2 = psycho_meta_red$tau2,
  Prediction_Lower = pred_red$pi.lb,
  Prediction_Upper = pred_red$pi.ub
) %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  heterogeneity_stats,
  caption = "Heterogeneity and Prediction Interval Statistics"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ==================================================
# EXPLORATORY UNIVARIABLE MODERATOR MODELS
# ==================================================

# Due to the small number of independent studies,
# separate univariable moderator models are used.
# Duration and hypoxia type are not examined.


# -----------------------------
# SEVERITY MODERATOR
# -----------------------------

psycho_severity <- rma.mv(
  yi,
  vi,
  mods = ~ Severity_c,
  random = ~ 1 | study,
  data = psycho_data,
  method = "REML"
)


# -----------------------------
# AGE MODERATOR
# -----------------------------

psycho_age <- rma.mv(
  yi,
  vi,
  mods = ~ Age_c,
  random = ~ 1 | study,
  data = psycho_data,
  method = "REML"
)


# ==================================================
# FUNCTION TO EXTRACT MODERATOR RESULTS
# ==================================================

extract_mod_results <- function(model, model_name) {
  
  model_summary <- summary(model)
  
  results <- data.frame(
    Moderator_Model = model_name,
    Term = rownames(model_summary$beta),
    Estimate = model_summary$beta[, 1],
    SE = model_summary$se,
    zval = model_summary$zval,
    pval = model_summary$pval,
    CI_Lower = model_summary$ci.lb,
    CI_Upper = model_summary$ci.ub
  )
  
  results$Term <- gsub(
    "intrcpt",
    "Intercept",
    results$Term
  )
  
  results$Term <- gsub(
    "Severity_c",
    "Severity",
    results$Term
  )
  
  results$Term <- gsub(
    "Age_c",
    "Age",
    results$Term
  )
  
  results %>%
    mutate(
      across(
        where(is.numeric),
        round,
        digits = 3
      )
    )
}


# -----------------------------
# EXTRACT MODERATOR RESULTS
# -----------------------------

severity_results <- extract_mod_results(
  psycho_severity,
  "Severity"
)

age_results <- extract_mod_results(
  psycho_age,
  "Age"
)


# -----------------------------
# COMBINE MODERATOR RESULTS
# -----------------------------

moderator_results <- bind_rows(
  severity_results,
  age_results
)


kable(
  moderator_results,
  caption = "Exploratory Univariable Moderator Models: Psychomotor Speed"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ==================================================
# MODERATOR MODEL FIT STATISTICS
# ==================================================

moderator_fit <- data.frame(
  
  Model = c(
    "Severity",
    "Age"
  ),
  
  Effect_Sizes = c(
    psycho_severity$k,
    psycho_age$k
  ),
  
  Studies = c(
    n_distinct(
      psycho_data %>%
        filter(!is.na(Severity_c)) %>%
        pull(study)
    ),
    
    n_distinct(
      psycho_data %>%
        filter(!is.na(Age_c)) %>%
        pull(study)
    )
  ),
  
  QM = c(
    psycho_severity$QM,
    psycho_age$QM
  ),
  
  QM_df = c(
    psycho_severity$m,
    psycho_age$m
  ),
  
  QM_p = c(
    psycho_severity$QMp,
    psycho_age$QMp
  ),
  
  QE = c(
    psycho_severity$QE,
    psycho_age$QE
  ),
  
  QE_df = c(
    psycho_severity$k - psycho_severity$p,
    psycho_age$k - psycho_age$p
  ),
  
  QE_p = c(
    psycho_severity$QEp,
    psycho_age$QEp
  ),
  
  Tau2 = c(
    psycho_severity$sigma2,
    psycho_age$sigma2
  )
) %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  moderator_fit,
  caption = "Model Fit Statistics for Exploratory Moderator Models"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ==================================================
# DATA CONTRIBUTING TO MODERATOR MODELS
# ==================================================

moderator_k <- data.frame(
  
  Model = c(
    "Severity",
    "Age"
  ),
  
  Effect_Sizes = c(
    nrow(
      psycho_data %>%
        filter(!is.na(Severity_c))
    ),
    
    nrow(
      psycho_data %>%
        filter(!is.na(Age_c))
    )
  ),
  
  Studies = c(
    psycho_data %>%
      filter(!is.na(Severity_c)) %>%
      summarise(n = n_distinct(study)) %>%
      pull(n),
    
    psycho_data %>%
      filter(!is.na(Age_c)) %>%
      summarise(n = n_distinct(study)) %>%
      pull(n)
  )
)


kable(
  moderator_k,
  caption = "Data Contributing to Exploratory Moderator Models"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ==================================================
# FUNNEL PLOT
# ==================================================

funnel(
  psycho_meta_red,
  main = "Funnel Plot: Psychomotor Speed (Gps)"
)


# ==================================================
# TRIM-AND-FILL MODEL
# ==================================================

tf_model <- trimfill(
  psycho_meta_red
)

tf_summary <- summary(
  tf_model
)


# -----------------------------
# TRIM-AND-FILL EFFECT
# -----------------------------

tf_model_stats <- data.frame(
  Term = "Trim-and-Fill Effect",
  Estimate = tf_summary$beta[, 1],
  SE = tf_summary$se,
  zval = tf_summary$zval,
  pval = tf_summary$pval,
  CI_Lower = tf_summary$ci.lb,
  CI_Upper = tf_summary$ci.ub
) %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  tf_model_stats,
  caption = "Trim-and-Fill Corrected Model: Psychomotor Speed"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# -----------------------------
# TRIM-AND-FILL IMPUTATION RESULTS
# -----------------------------

trimfill_counts <- data.frame(
  Original_Effect_Sizes = psycho_meta_red$k,
  Imputed_Effect_Sizes = tf_model$k0,
  Total_Effect_Sizes = psycho_meta_red$k + tf_model$k0
)


kable(
  trimfill_counts,
  caption = "Trim-and-Fill Imputation Results"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )
```

# Processing speed
```{r}
# ==================================================
# PROCESSING SPEED (Gs)
# ==================================================

# -----------------------------
# SUBSET DATA
# -----------------------------

speed_data <- cog_ability_filt %>%
  filter(chc_code == "gs")


# Create complete-case dataset for duration moderator
speed_duration_data <- speed_data %>%
  filter(!is.na(log_duration_c))


# ==================================================
# MAIN EFFECT MODEL
# ==================================================

speed_meta_red <- rma(
  yi = yi,
  vi = vi,
  data = speed_data,
  method = "REML"
)


# -----------------------------
# MAIN EFFECT RESULTS
# -----------------------------

summary_red <- summary(speed_meta_red)

model_stats <- data.frame(
  Term = "Overall Effect",
  Estimate = summary_red$beta[, 1],
  SE = summary_red$se,
  zval = summary_red$zval,
  pval = summary_red$pval,
  CI_Lower = summary_red$ci.lb,
  CI_Upper = summary_red$ci.ub
) %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  model_stats,
  caption = "Main Effect Model: Processing Speed"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ==================================================
# HETEROGENEITY STATISTICS
# ==================================================

# Calculate 95% prediction interval
pred_red <- predict(
  speed_meta_red,
  pi = TRUE
)


heterogeneity_stats <- data.frame(
  Effect_Sizes = speed_meta_red$k,
  Studies = n_distinct(speed_data$study),
  QE = speed_meta_red$QE,
  QE_df = speed_meta_red$k - 1,
  QE_p = speed_meta_red$QEp,
  I2 = speed_meta_red$I2,
  Tau2 = speed_meta_red$tau2,
  Prediction_Lower = pred_red$pi.lb,
  Prediction_Upper = pred_red$pi.ub
) %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  heterogeneity_stats,
  caption = "Heterogeneity and Prediction Interval Statistics"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down")
  )


# ==================================================
# EXPLORATORY UNIVARIABLE MODERATOR MODELS
# ==================================================

# Univariable mixed-effects meta-regressions were used.
# Hypoxia type was not included because the four-level
# factor contained sparse categories.


# -----------------------------
# SEVERITY MODERATOR
# -----------------------------

speed_severity <- rma.mv(
  yi,
  vi,
  mods = ~ Severity_c,
  random = ~ 1 | study,
  data = speed_data,
  method = "REML"
)


# -----------------------------
# DURATION MODERATOR
# -----------------------------
# Complete cases only

speed_duration <- rma.mv(
  yi,
  vi,
  mods = ~ log_duration_c,
  random = ~ 1 | study,
  data = speed_duration_data,
  method = "REML"
)


# -----------------------------
# AGE MODERATOR
# -----------------------------

speed_age <- rma.mv(
  yi,
  vi,
  mods = ~ Age_c,
  random = ~ 1 | study,
  data = speed_data,
  method = "REML"
)


# ==================================================
# FUNCTION TO EXTRACT MODERATOR RESULTS
# ==================================================

extract_mod_results <- function(model, model_name) {
  
  model_summary <- summary(model)
  
  results <- data.frame(
    Moderator_Model = model_name,
    Term = rownames(model_summary$beta),
    Estimate = model_summary$beta[, 1],
    SE = model_summary$se,
    zval = model_summary$zval,
    pval = model_summary$pval,
    CI_Lower = model_summary$ci.lb,
    CI_Upper = model_summary$ci.ub
  )
  
  # Improve intercept label
  results$Term <- gsub(
    "intrcpt",
    "Intercept",
    results$Term
  )
  
  # Improve moderator labels
  results$Term <- gsub(
    "Severity_c",
    "Severity",
    results$Term
  )
  
  results$Term <- gsub(
    "log_duration_c",
    "Log Duration",
    results$Term
  )
  
  results$Term <- gsub(
    "Age_c",
    "Age",
    results$Term
  )
  
  results %>%
    mutate(
      across(
        where(is.numeric),
        round,
        digits = 3
      )
    )
}


# ==================================================
# EXTRACT MODERATOR RESULTS
# ==================================================

severity_results <- extract_mod_results(
  speed_severity,
  "Severity"
)


duration_results <- extract_mod_results(
  speed_duration,
  "Duration"
)


age_results <- extract_mod_results(
  speed_age,
  "Age"
)


# ==================================================
# COMBINE MODERATOR RESULTS
# ==================================================

moderator_results <- bind_rows(
  severity_results,
  duration_results,
  age_results
)


kable(
  moderator_results,
  caption = "Exploratory Univariable Moderator Models: Processing Speed"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ==================================================
# MODERATOR MODEL FIT STATISTICS
# ==================================================

moderator_fit <- data.frame(
  
  Model = c(
    "Severity",
    "Duration",
    "Age"
  ),
  
  Effect_Sizes = c(
    speed_severity$k,
    speed_duration$k,
    speed_age$k
  ),
  
  Studies = c(
    n_distinct(
      speed_data %>%
        filter(!is.na(Severity_c)) %>%
        pull(study)
    ),
    
    n_distinct(
      speed_duration_data %>%
        pull(study)
    ),
    
    n_distinct(
      speed_data %>%
        filter(!is.na(Age_c)) %>%
        pull(study)
    )
  ),
  
  QM = c(
    speed_severity$QM,
    speed_duration$QM,
    speed_age$QM
  ),
  
  QM_df = c(
    speed_severity$m,
    speed_duration$m,
    speed_age$m
  ),
  
  QM_p = c(
    speed_severity$QMp,
    speed_duration$QMp,
    speed_age$QMp
  ),
  
  QE = c(
    speed_severity$QE,
    speed_duration$QE,
    speed_age$QE
  ),
  
  QE_df = c(
    speed_severity$k - speed_severity$p,
    speed_duration$k - speed_duration$p,
    speed_age$k - speed_age$p
  ),
  
  QE_p = c(
    speed_severity$QEp,
    speed_duration$QEp,
    speed_age$QEp
  ),
  
  Tau2 = c(
    speed_severity$sigma2,
    speed_duration$sigma2,
    speed_age$sigma2
  )
) %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  moderator_fit,
  caption = "Model Fit Statistics for Exploratory Moderator Models"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ==================================================
# DATA CONTRIBUTING TO MODERATOR MODELS
# ==================================================

moderator_k <- data.frame(
  
  Model = c(
    "Severity",
    "Duration",
    "Age"
  ),
  
  Effect_Sizes = c(
    nrow(
      speed_data %>%
        filter(!is.na(Severity_c))
    ),
    
    nrow(speed_duration_data),
    
    nrow(
      speed_data %>%
        filter(!is.na(Age_c))
    )
  ),
  
  Studies = c(
    speed_data %>%
      filter(!is.na(Severity_c)) %>%
      summarise(n = n_distinct(study)) %>%
      pull(n),
    
    speed_duration_data %>%
      summarise(n = n_distinct(study)) %>%
      pull(n),
    
    speed_data %>%
      filter(!is.na(Age_c)) %>%
      summarise(n = n_distinct(study)) %>%
      pull(n)
  )
)


kable(
  moderator_k,
  caption = "Data Contributing to Exploratory Moderator Models"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ==================================================
# FUNNEL PLOT
# ==================================================

funnel(
  speed_meta_red,
  main = "Funnel Plot: Processing Speed (Gs)"
)


# ==================================================
# TRIM-AND-FILL MODEL
# ==================================================

tf_model <- trimfill(
  speed_meta_red
)

tf_summary <- summary(
  tf_model
)


# -----------------------------
# TRIM-AND-FILL EFFECT
# -----------------------------

tf_model_stats <- data.frame(
  Term = "Trim-and-Fill Effect",
  Estimate = tf_summary$beta[, 1],
  SE = tf_summary$se,
  zval = tf_summary$zval,
  pval = tf_summary$pval,
  CI_Lower = tf_summary$ci.lb,
  CI_Upper = tf_summary$ci.ub
) %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  tf_model_stats,
  caption = "Trim-and-Fill Corrected Model: Processing Speed"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# -----------------------------
# TRIM-AND-FILL IMPUTATION RESULTS
# -----------------------------

trimfill_counts <- data.frame(
  Original_Effect_Sizes = speed_meta_red$k,
  Imputed_Effect_Sizes = tf_model$k0,
  Total_Effect_Sizes = speed_meta_red$k + tf_model$k0
)


kable(
  trimfill_counts,
  caption = "Trim-and-Fill Imputation Results"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )
```

# Short-term memory (Gsm)
```{r}

# ==================================================
# SUBSET DATA
# ==================================================

short_data <- cog_ability_filt %>%
  filter(chc_code == "gsm")

# Complete-case datasets for moderator analyses
short_severity_data <- short_data %>%
  filter(!is.na(Severity_c))

short_duration_data <- short_data %>%
  filter(!is.na(log_duration_c))

short_age_data <- short_data %>%
  filter(!is.na(Age_c))

# Restrict hypoxia type analysis to adequately represented categories
short_type_data <- short_data %>%
  filter(
    T.2 %in% c("hypobaric hypoxia", "normobaric hypoxia")
  ) %>%
  droplevels()


# ==================================================
# MAIN EFFECT MODEL
# ==================================================

short_meta_red <- rma(
  yi = yi,
  vi = vi,
  data = short_data,
  method = "REML"
)

summary_red <- summary(short_meta_red)

# -----------------------------
# Main effect coefficient
# -----------------------------

model_stats <- data.frame(
  Term = "Overall Effect",
  Estimate = summary_red$beta[, 1],
  SE = summary_red$se,
  zval = summary_red$zval,
  pval = summary_red$pval,
  CI_Lower = summary_red$ci.lb,
  CI_Upper = summary_red$ci.ub
) %>%
  mutate(across(where(is.numeric), round, digits = 3))


kable(
  model_stats,
  caption = "Main Effect Model: Short-Term Memory (Gsm)"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ==================================================
# MAIN EFFECT MODEL FIT AND HETEROGENEITY
# ==================================================

# 95% prediction interval
short_pred <- predict(short_meta_red, level = 95)

main_fit_stats <- data.frame(
  Statistic = c(
    "Effect Sizes (k)",
    "Independent Studies",
    "Q",
    "Q df",
    "Q p-value",
    "I² (%)",
    "Tau²",
    "Tau",
    "95% Prediction Interval Lower",
    "95% Prediction Interval Upper"
  ),

  Value = c(
    short_meta_red$k,
    n_distinct(short_data$study),
    short_meta_red$QE,
    short_meta_red$k - short_meta_red$p,
    short_meta_red$QEp,
    short_meta_red$I2,
    short_meta_red$tau2,
    sqrt(short_meta_red$tau2),
    short_pred$pi.lb,
    short_pred$pi.ub
  )
) %>%
  mutate(
    Value = round(Value, 3)
  )


kable(
  main_fit_stats,
  caption = "Model Fit and Heterogeneity Statistics: Short-Term Memory (Gsm)"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ==================================================
# EXPLORATORY UNIVARIABLE MODERATOR MODELS
# ==================================================


# --------------------------------------------------
# Severity moderator
# --------------------------------------------------

short_severity <- rma.mv(
  yi,
  vi,
  mods = ~ Severity_c,
  random = ~ 1 | study,
  data = short_severity_data,
  method = "REML"
)


# --------------------------------------------------
# Duration moderator
# --------------------------------------------------

short_duration <- rma.mv(
  yi,
  vi,
  mods = ~ log_duration_c,
  random = ~ 1 | study,
  data = short_duration_data,
  method = "REML"
)


# --------------------------------------------------
# Age moderator
# --------------------------------------------------

short_age <- rma.mv(
  yi,
  vi,
  mods = ~ Age_c,
  random = ~ 1 | study,
  data = short_age_data,
  method = "REML"
)


# --------------------------------------------------
# Hypoxia type moderator
# --------------------------------------------------

short_type <- rma.mv(
  yi,
  vi,
  mods = ~ T.2,
  random = ~ 1 | study,
  data = short_type_data,
  method = "REML"
)


# ==================================================
# FUNCTION TO EXTRACT MODERATOR RESULTS
# ==================================================

extract_moderator_results <- function(model, model_name) {

  model_summary <- summary(model)

  data.frame(
    Moderator_Model = model_name,
    Term = rownames(model_summary$beta),
    Estimate = model_summary$beta[, 1],
    SE = model_summary$se,
    zval = model_summary$zval,
    pval = model_summary$pval,
    CI_Lower = model_summary$ci.lb,
    CI_Upper = model_summary$ci.ub
  )
}


# ==================================================
# EXTRACT COEFFICIENT RESULTS
# ==================================================

severity_results <- extract_moderator_results(
  short_severity,
  "Severity"
)

duration_results <- extract_moderator_results(
  short_duration,
  "Duration"
)

age_results <- extract_moderator_results(
  short_age,
  "Age"
)

type_results <- extract_moderator_results(
  short_type,
  "Hypoxia Type"
)


# ==================================================
# CLEAN TERM LABELS
# ==================================================

moderator_results <- bind_rows(
  severity_results,
  duration_results,
  age_results,
  type_results
) %>%
  mutate(
    Term = case_when(
      Term == "intrcpt" ~ "Intercept",
      Term == "Severity_c" ~ "Severity",
      Term == "log_duration_c" ~ "Log Duration",
      Term == "Age_c" ~ "Age",
      grepl("T\\.2", Term) ~
        gsub("T\\.2", "Hypoxia Type: ", Term),
      TRUE ~ Term
    )
  ) %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  moderator_results,
  caption = "Exploratory Univariable Moderator Models: Short-Term Memory (Gsm)"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ==================================================
# MODERATOR MODEL FIT STATISTICS
# ==================================================

extract_model_fit <- function(model, model_name, data) {

  model_summary <- summary(model)

  data.frame(
    Model = model_name,
    Effect_Sizes = model$k,
    Studies = n_distinct(data$study),
    QE = model$QE,
    QE_df = model$k - model$p,
    QE_p = model$QEp,
    QM = model$QM,
    QM_df = model$p - 1,
    QM_p = model$QMp,
    AIC = AIC(model),
    BIC = BIC(model),
    LogLik = as.numeric(logLik(model)),
    Tau2 = sum(model$sigma2)
  )
}


severity_fit <- extract_model_fit(
  short_severity,
  "Severity",
  short_severity_data
)

duration_fit <- extract_model_fit(
  short_duration,
  "Duration",
  short_duration_data
)

age_fit <- extract_model_fit(
  short_age,
  "Age",
  short_age_data
)

type_fit <- extract_model_fit(
  short_type,
  "Hypoxia Type",
  short_type_data
)


moderator_fit_stats <- bind_rows(
  severity_fit,
  duration_fit,
  age_fit,
  type_fit
) %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  moderator_fit_stats,
  caption = "Model Fit Statistics for Exploratory Moderator Models: Short-Term Memory (Gsm)"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ==================================================
# NUMBER OF EFFECT SIZES AND STUDIES
# CONTRIBUTING TO EACH MODERATOR MODEL
# ==================================================

moderator_k <- data.frame(
  Model = c(
    "Severity",
    "Duration",
    "Age",
    "Hypoxia Type"
  ),

  Effect_Sizes = c(
    nrow(short_severity_data),
    nrow(short_duration_data),
    nrow(short_age_data),
    nrow(short_type_data)
  ),

  Studies = c(
    n_distinct(short_severity_data$study),
    n_distinct(short_duration_data$study),
    n_distinct(short_age_data$study),
    n_distinct(short_type_data$study)
  )
)


kable(
  moderator_k,
  caption = "Data Contributing to Exploratory Moderator Models: Short-Term Memory (Gsm)"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ==================================================
# FUNNEL PLOT
# ==================================================

funnel(
  short_meta_red,
  main = "Funnel Plot: Short-Term Memory (Gsm)"
)


# ==================================================
# TRIM-AND-FILL MODEL
# ==================================================

tf_model <- trimfill(short_meta_red)

tf_summary <- summary(tf_model)


# -----------------------------
# Trim-and-fill coefficient
# -----------------------------

tf_model_stats <- data.frame(
  Term = "Trim-and-Fill Effect",
  Estimate = tf_summary$beta[, 1],
  SE = tf_summary$se,
  zval = tf_summary$zval,
  pval = tf_summary$pval,
  CI_Lower = tf_summary$ci.lb,
  CI_Upper = tf_summary$ci.ub
) %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  tf_model_stats,
  caption = "Trim-and-Fill Corrected Model: Short-Term Memory (Gsm)"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# -----------------------------
# Number of imputed studies
# -----------------------------

trimfill_stats <- data.frame(
  Statistic = c(
    "Observed Effect Sizes",
    "Imputed Effect Sizes",
    "Total Effect Sizes After Trim-and-Fill"
  ),

  Value = c(
    short_meta_red$k,
    tf_model$k0,
    tf_model$k
  )
)


kable(
  trimfill_stats,
  caption = "Trim-and-Fill Imputation Summary: Short-Term Memory (Gsm)"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )
```

# Decision speed / reaction time (Gt)
```{r}

# ==================================================
# SUBSET DATA
# ==================================================

decision_data <- cog_ability_filt %>%
  filter(chc_code == "gt")


# Complete-case datasets for moderator analyses

decision_severity_data <- decision_data %>%
  filter(!is.na(Severity_c))

# No missing duration data for Gt, but defining this
# explicitly keeps the framework consistent
decision_duration_data <- decision_data %>%
  filter(!is.na(log_duration_c))

decision_age_data <- decision_data %>%
  filter(!is.na(Age_c))


# Restrict hypoxia type analysis to the two adequately
# represented categories

decision_type_data <- decision_data %>%
  filter(
    T.2 %in% c(
      "hypobaric hypoxia",
      "normobaric hypoxia"
    )
  ) %>%
  droplevels()


# ==================================================
# MAIN EFFECT MODEL
# ==================================================

decision_meta_red <- rma(
  yi = yi,
  vi = vi,
  data = decision_data,
  method = "REML"
)


summary_red <- summary(decision_meta_red)


# -----------------------------
# Main effect coefficient
# -----------------------------

model_stats <- data.frame(
  Term = "Overall Effect",
  Estimate = summary_red$beta[, 1],
  SE = summary_red$se,
  zval = summary_red$zval,
  pval = summary_red$pval,
  CI_Lower = summary_red$ci.lb,
  CI_Upper = summary_red$ci.ub
) %>%
  mutate(
    across(where(is.numeric), round, digits = 3)
  )


kable(
  model_stats,
  caption = "Main Effect Model: Decision Speed / Reaction Time (Gt)"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ==================================================
# MAIN EFFECT MODEL FIT AND HETEROGENEITY
# ==================================================

# 95% prediction interval

decision_pred <- predict(
  decision_meta_red,
  level = 95
)


main_fit_stats <- data.frame(
  Statistic = c(
    "Effect Sizes (k)",
    "Independent Studies",
    "Q",
    "Q df",
    "Q p-value",
    "I² (%)",
    "Tau²",
    "Tau",
    "95% Prediction Interval Lower",
    "95% Prediction Interval Upper"
  ),

  Value = c(
    decision_meta_red$k,
    n_distinct(decision_data$study),
    decision_meta_red$QE,
    decision_meta_red$k - decision_meta_red$p,
    decision_meta_red$QEp,
    decision_meta_red$I2,
    decision_meta_red$tau2,
    sqrt(decision_meta_red$tau2),
    decision_pred$pi.lb,
    decision_pred$pi.ub
  )
) %>%
  mutate(
    Value = round(Value, 3)
  )


kable(
  main_fit_stats,
  caption = "Model Fit and Heterogeneity Statistics: Decision Speed / Reaction Time (Gt)"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ==================================================
# EXPLORATORY UNIVARIABLE MODERATOR MODELS
# ==================================================


# --------------------------------------------------
# Severity moderator
# --------------------------------------------------

decision_severity <- rma.mv(
  yi,
  vi,
  mods = ~ Severity_c,
  random = ~ 1 | study,
  data = decision_severity_data,
  method = "REML"
)


# --------------------------------------------------
# Duration moderator
# --------------------------------------------------

decision_duration <- rma.mv(
  yi,
  vi,
  mods = ~ log_duration_c,
  random = ~ 1 | study,
  data = decision_duration_data,
  method = "REML"
)


# --------------------------------------------------
# Age moderator
# --------------------------------------------------

decision_age <- rma.mv(
  yi,
  vi,
  mods = ~ Age_c,
  random = ~ 1 | study,
  data = decision_age_data,
  method = "REML"
)


# --------------------------------------------------
# Hypoxia type moderator
# --------------------------------------------------

decision_type <- rma.mv(
  yi,
  vi,
  mods = ~ T.2,
  random = ~ 1 | study,
  data = decision_type_data,
  method = "REML"
)


# ==================================================
# FUNCTION TO EXTRACT MODERATOR RESULTS
# ==================================================

extract_moderator_results <- function(model, model_name) {

  model_summary <- summary(model)

  data.frame(
    Moderator_Model = model_name,
    Term = rownames(model_summary$beta),
    Estimate = model_summary$beta[, 1],
    SE = model_summary$se,
    zval = model_summary$zval,
    pval = model_summary$pval,
    CI_Lower = model_summary$ci.lb,
    CI_Upper = model_summary$ci.ub
  )
}


# ==================================================
# EXTRACT COEFFICIENT RESULTS
# ==================================================

severity_results <- extract_moderator_results(
  decision_severity,
  "Severity"
)

duration_results <- extract_moderator_results(
  decision_duration,
  "Duration"
)

age_results <- extract_moderator_results(
  decision_age,
  "Age"
)

type_results <- extract_moderator_results(
  decision_type,
  "Hypoxia Type"
)


# ==================================================
# COMBINE AND CLEAN MODERATOR RESULTS
# ==================================================

moderator_results <- bind_rows(
  severity_results,
  duration_results,
  age_results,
  type_results
) %>%
  mutate(
    Term = case_when(
      Term == "intrcpt" ~ "Intercept",
      Term == "Severity_c" ~ "Severity",
      Term == "log_duration_c" ~ "Log Duration",
      Term == "Age_c" ~ "Age",
      grepl("T\\.2", Term) ~
        gsub("T\\.2", "Hypoxia Type: ", Term),
      TRUE ~ Term
    )
  ) %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  moderator_results,
  caption = "Exploratory Univariable Moderator Models: Decision Speed / Reaction Time (Gt)"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ==================================================
# MODERATOR MODEL FIT STATISTICS
# ==================================================

extract_model_fit <- function(model, model_name, data) {

  data.frame(
    Model = model_name,
    Effect_Sizes = model$k,
    Studies = n_distinct(data$study),
    QE = model$QE,
    QE_df = model$k - model$p,
    QE_p = model$QEp,
    QM = model$QM,
    QM_df = model$p - 1,
    QM_p = model$QMp,
    AIC = AIC(model),
    BIC = BIC(model),
    LogLik = as.numeric(logLik(model)),
    Variance_Component = sum(model$sigma2)
  )
}


severity_fit <- extract_model_fit(
  decision_severity,
  "Severity",
  decision_severity_data
)

duration_fit <- extract_model_fit(
  decision_duration,
  "Duration",
  decision_duration_data
)

age_fit <- extract_model_fit(
  decision_age,
  "Age",
  decision_age_data
)

type_fit <- extract_model_fit(
  decision_type,
  "Hypoxia Type",
  decision_type_data
)


moderator_fit_stats <- bind_rows(
  severity_fit,
  duration_fit,
  age_fit,
  type_fit
) %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  moderator_fit_stats,
  caption = "Model Fit Statistics for Exploratory Moderator Models: Decision Speed / Reaction Time (Gt)"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ==================================================
# NUMBER OF EFFECT SIZES AND STUDIES CONTRIBUTING
# ==================================================

moderator_k <- data.frame(
  Model = c(
    "Severity",
    "Duration",
    "Age",
    "Hypoxia Type"
  ),

  Effect_Sizes = c(
    nrow(decision_severity_data),
    nrow(decision_duration_data),
    nrow(decision_age_data),
    nrow(decision_type_data)
  ),

  Studies = c(
    n_distinct(decision_severity_data$study),
    n_distinct(decision_duration_data$study),
    n_distinct(decision_age_data$study),
    n_distinct(decision_type_data$study)
  )
)


kable(
  moderator_k,
  caption = "Data Contributing to Exploratory Moderator Models: Decision Speed / Reaction Time (Gt)"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ==================================================
# FUNNEL PLOT
# ==================================================

funnel(
  decision_meta_red,
  main = "Funnel Plot: Decision Speed / Reaction Time (Gt)"
)


# ==================================================
# TRIM-AND-FILL MODEL
# ==================================================

tf_model <- trimfill(decision_meta_red)

tf_summary <- summary(tf_model)


# -----------------------------
# Trim-and-fill coefficient
# -----------------------------

tf_model_stats <- data.frame(
  Term = "Trim-and-Fill Effect",
  Estimate = tf_summary$beta[, 1],
  SE = tf_summary$se,
  zval = tf_summary$zval,
  pval = tf_summary$pval,
  CI_Lower = tf_summary$ci.lb,
  CI_Upper = tf_summary$ci.ub
) %>%
  mutate(
    across(
      where(is.numeric),
      round,
      digits = 3
    )
  )


kable(
  tf_model_stats,
  caption = "Trim-and-Fill Corrected Model: Decision Speed / Reaction Time (Gt)"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ==================================================
# TRIM-AND-FILL IMPUTATION SUMMARY
# ==================================================

trimfill_stats <- data.frame(
  Statistic = c(
    "Observed Effect Sizes",
    "Imputed Effect Sizes",
    "Total Effect Sizes After Trim-and-Fill"
  ),

  Value = c(
    decision_meta_red$k,
    tf_model$k0,
    tf_model$k
  )
)


kable(
  trimfill_stats,
  caption = "Trim-and-Fill Imputation Summary: Decision Speed / Reaction Time (Gt)"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )
```

# Visual processing (Gv)
```{r}

# ============================================================
# SUBSET DATA
# ============================================================

visual_data <- cog_ability_filt %>%
  filter(chc_code == "gv")


# ============================================================
# MAIN EFFECT MODEL
# ============================================================

visual_meta_red <- rma(
  yi = yi,
  vi = vi,
  data = visual_data,
  method = "REML"
)


# ============================================================
# EXTRACT MAIN EFFECT RESULTS
# ============================================================

summary_red <- summary(visual_meta_red)

model_stats <- data.frame(
  Term      = "Overall effect",
  Estimate  = as.numeric(summary_red$beta),
  SE        = summary_red$se,
  zval      = summary_red$zval,
  pval      = summary_red$pval,
  CI_Lower  = summary_red$ci.lb,
  CI_Upper  = summary_red$ci.ub
)

model_stats <- model_stats %>%
  mutate(across(where(is.numeric), round, digits = 3))


kable(
  model_stats,
  caption = "Main Effect Model: Visual Processing"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ============================================================
# MODEL FIT, HETEROGENEITY, AND PREDICTION INTERVAL
# ============================================================

# Number of effect sizes
k_effect_sizes <- visual_meta_red$k

# Number of unique studies
k_studies <- n_distinct(visual_data$study)

# Heterogeneity statistics
heterogeneity_stats <- data.frame(
  Statistic = c(
    "Effect sizes",
    "Independent studies",
    "Tau squared",
    "Tau",
    "I squared (%)",
    "Q",
    "Q df",
    "Q p-value"
  ),
  
  Value = c(
    k_effect_sizes,
    k_studies,
    visual_meta_red$tau2,
    sqrt(visual_meta_red$tau2),
    visual_meta_red$I2,
    visual_meta_red$QE,
    visual_meta_red$k - visual_meta_red$p,
    visual_meta_red$QEp
  )
)


# Round numeric values
heterogeneity_stats <- heterogeneity_stats %>%
  mutate(
    Value = case_when(
      Statistic == "Q p-value" ~ format.pval(
        as.numeric(Value),
        digits = 3,
        eps = 0.001
      ),
      TRUE ~ as.character(round(as.numeric(Value), 3))
    )
  )


kable(
  heterogeneity_stats,
  caption = "Heterogeneity Statistics: Visual Processing"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ============================================================
# PREDICTION INTERVAL
# ============================================================

# Prediction interval for the random-effects model
pred_interval <- predict(visual_meta_red)

prediction_interval <- data.frame(
  Estimate = round(pred_interval$pred, 3),
  PI_Lower = round(pred_interval$pi.lb, 3),
  PI_Upper = round(pred_interval$pi.ub, 3)
)


kable(
  prediction_interval,
  caption = "Prediction Interval: Visual Processing"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ============================================================
# MODERATOR ANALYSES
# ============================================================

# Moderator analyses were not conducted because visual processing
# included only 4 independent studies. Meta-regression with this
# number of studies would be substantially underpowered and likely
# to produce unstable estimates.
#
# Hypoxia type was also not examined because the distribution was
# highly imbalanced across categories. Therefore, no meaningful
# comparison between hypoxia types could be conducted.


# ============================================================
# FUNNEL PLOT
# ============================================================

# Interpret with extreme caution due to the small number of
# independent studies. Funnel plot asymmetry cannot be meaningfully
# assessed with only 4 studies.

funnel(
  visual_meta_red,
  main = "Funnel Plot: Visual Processing (Gv)"
)


# ============================================================
# TRIM-AND-FILL MODEL
# ============================================================

# Trim-and-fill is exploratory only because the analysis includes
# very few independent studies and estimates from this procedure
# are unreliable with such a small k.

tf_model <- trimfill(visual_meta_red)

tf_summary <- summary(tf_model)

tf_model_stats <- data.frame(
  Term      = "Trim-and-fill adjusted effect",
  Estimate  = as.numeric(tf_summary$beta),
  SE        = tf_summary$se,
  zval      = tf_summary$zval,
  pval      = tf_summary$pval,
  CI_Lower  = tf_summary$ci.lb,
  CI_Upper  = tf_summary$ci.ub
)

tf_model_stats <- tf_model_stats %>%
  mutate(across(where(is.numeric), round, digits = 3))


kable(
  tf_model_stats,
  caption = "Trim-and-Fill Corrected Model: Visual Processing"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )


# ============================================================
# TRIM-AND-FILL DIAGNOSTICS
# ============================================================

trimfill_diagnostics <- data.frame(
  Statistic = c(
    "Observed effect sizes",
    "Imputed effect sizes",
    "Total effect sizes"
  ),
  
  Value = c(
    visual_meta_red$k,
    tf_model$k0,
    tf_model$k
  )
)


kable(
  trimfill_diagnostics,
  caption = "Trim-and-Fill Diagnostics: Visual Processing"
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position")
  )
```